---
title: "textclass"
author: "Charter Sevier"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{textclass}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, cache=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
This vignette outlines the intended use of the textclass package in its current form. The package is able to:

- Create Document-Term Matrices in tidy form
- Evaluate Term Frequency and N-gram Frequency
- Graphically portray latent topic metrics for each number of topics 2 to 30
  - Return raw Cao and Deveaud metrics
  - Return normalized metrics
  - Rank order the metrics to show list of potential optimal topic candidates
- Model Topics for given number of topics, K

## Provided Data

  This package includes `AFICAdata` dataset. It is a dataframe of all Information Technology contracts for installation support from Air Force Installation Contracting Agency.

## term_frequency

  The `term_frequency` function allows the user to plot term or n-gram frequency depending on how many consecutive terms (`n`) for which they wish to evaluate term frequency.

```{r, echo = FALSE}
library(textclass)
```

```{r, echo = TRUE}
term_frequency(AFICAdata, n=3)
```

## tidyDTM

The `tidyDTM` function allows the user to construct a dtm for a given sparsity. 

```{r, echo = TRUE}
#tidyDTM(data, sparsity)
dtm <- tidyDTM(AFICAdata, 0.98)
dtm
```


## plot_topics

The `plot_topics` function allows the user to plot the topic models from a Latent Dirichlet Allocation (LDA) model. This plot shows the most associated (beta) terms with each of the topics. The `LDA` function is an external function for which the user can create the LDA model and define the number of topics requested.

```{r, echo = TRUE}
lda <- LDA(dtm, k = 4)
plot_topics(lda)
```

## optimal_topics, normalize_metrics, and plot_optimal_topics

The functions `optimal_topics`, `normalize_metrics`, and `plot_optimal_topics`allow the use to evaluate the structure of topics for every number of topics k from 2 to 30. The metrics used are those proposed by Cao and Deveaud. Cao is a metric that needs to be minimized for optimality, while Deveaud is intended to be maximized. This takes very long without a quad-core computer. Fortunately, included with the package is pre-calculated optimal topic data, `topic_data`.

```{r, echo=TRUE}

#returns raw values for optimal topic analysis
#values <- optimal_topics(dtm)
values <- topic_data

#normalizes the values
norm_values <- normalize_metrics(values)
#plots the optimal topic analysis metrics
plot_optimal_topics(norm_values)
```

As the Cao metric needs to be minimized to find optimality and the Deveaud metric maximized, this package provides a table using `rank_topics` that will rank order the topics by the best balance between the two metrics for the analyst to assess all possible points of optimality.

```{r, echo = TRUE}
#creates a table of rank ordered topic numbers
rank_topics(norm_values)
```


